\documentclass{muratcan_cv}
\usepackage{setspace}
\usepackage{fontawesome}
\usepackage{hyperref}
\setstretch{1.25}
\setname{Berkay}{Demirören}
\setaddress{Turin/Italy}
\setmobile{+90 507 204 7759}
\setmail{berkay.demiroren@gmail.com}
\setposition{Part-time iOS Developer} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/kayberd/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/kayberd} %you can play with color of the template (red is also nice..)
\setthemecolor{black} %you can play with color of the template (red is also nice..)

\begin{document}
%Create header
\headerview 
\vspace{2ex}
%Sections
%

%Education
\section{Education} 
    \datedexperience{METU (Ankara/Turkey)}{2017 - 2022} 
    \explanation{\coloredbullet \ Computer Engineering B.S. (Honor Student)} 
    
    \datedexperience{Polytechnic University of Turin (Turin/Italy)}{2024 - Current} 
    \explanation{\coloredbullet \ Computer Engineering M.Sc.} 

%
% Experience
\section{Experience}
    \datedexperience{PetLeo GmbH  (germany) }{April 2022 - Current} 
    \explanation{Flutter Developer}
    \explanationdetail{\scriptsize \vspace{4pt} 
    \coloredbullet \hspace{3pt} Developing cross-platform mobile and web apps for pet owners and veterinarians. \newline
    \coloredbullet \hspace{3pt} rxdart, get\_it, go\_router, chopper, hive, sentry,  mockito, flutter\_test, flutter\_driver, sonarqube, deeplinking  \vspace{10pt}}
    %
    \datedexperience{Inofab Health Tech. Inc.  (turkey)}{January - October 2022 (10 Months)} 
    \explanation{Intern iOS Developer}
    \explanationdetail{\scriptsize \vspace{4pt} 
    \coloredbullet \hspace{3pt} Developed an iOS app to enable interaction between patient and inhaler devices.\newline
    \coloredbullet \hspace{3pt} UIKit, REST, CocoaPods, SonarQube, MVM \vspace{10pt}}

    
    
    \vspace{10pt}}
    %
% Projects
\section{Projects}
    \datedexperience{Intelligent Library Monitoring System \href{https://github.com/kayberd/ilmos}{\color{black}\faicon{github}}}{}
    \explanationdetail{\scriptsize \vspace{8pt}
        \coloredbullet \hspace{3pt} Intelligent Library Monitoring System (ILMoS) is a deep learning guided project that improves library and study hall experience of users, enables efficient use of libraries, and minimizes abuse of desks. \newline
        \coloredbullet \hspace{3pt} ILMoS placed 4th over 24 senior projects at CENG DemoDay 2022. \newline
    }

%
% Volunteering
\section{Volunteering}
    \datedexperience{CYDD}{August 2020 - Current} 
    \explanation{Association for Supporting Contemporary Life - Edremit} 
    \explanationdetail{\scriptsize \vspace{8pt} \coloredbullet
    \hspace{3pt}The association was founded in 1989 by female medical doctor Turkan Saylan with the aim of providing children, especially girls, access to modern education. Today, the association provides grants and accommodation for students at various academic levels. As a scholar and volunteer, I assist with their IT needs.
   \vspace{10pt}}

%Footnote
\createfootnote
\end{document}
